Filter check

### 2019-01-14 R/filter-check.Rmd
Convert from ad-hoc package management to packrat
Break long pacbio reads into ITS1, ITS2 and LSU before dada, because the long reads are all singletons.  Save output of dada and derep into the same file.

```{r setup}
source("install_packages.R")

@@

```{r}
ggplot(datasets, aes(x = erate, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors per base") +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = eexp, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Expected number of errors") +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = length, group = Dataset, color = Dataset)) +
  stat_ecdf(geom = "step") +
  scale_x_log10(name = "Length (bp)") +
  scale_y_continuous(name = "Fraction Greater than length")

>>>>

```{r setup}
# source("install_packages.R")

@@

```{r}
library("scales")
reverselog_trans <- function(base = exp(1)) {
    trans <- function(x) -log(x, base)
    inv <- function(x) base^(-x)
    trans_new(paste0("reverselog-", format(base)), trans, inv, 
              log_breaks(base = base), 
              domain = c(1e-100, Inf))
}

ggplot(datasets, aes(x = erate, group = Dataset, color = Dataset)) +
  geom_step(aes(y = 1- ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors per base",
                     trans = reverselog_trans(10)) +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = eexp, group = Dataset, color = Dataset)) +
  geom_step(aes(y = 1- ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors",
                     trans = reverselog_trans(10)) +
  scale_y_continuous(name = "Fraction passing")

ggplot(datasets, aes(x = length, group = Dataset, color = Dataset)) +
  geom_step(aes(y = 1- ..y..), stat = "ecdf") +
  scale_x_log10(name = "Length (bp)") +
  scale_y_continuous(name = "Fraction Greater than length")

```
```{r}
datasets %>%
  group_by(Dataset) %>%
  do(out = dada2::plotQualityProfile(.$files, aggregate = TRUE) %>%
       print) %>%
  invisible
